---
title: "Superbowl TidyTuesday"
author: "Divyaanshu Panwar"
date: "3/3/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(tidytuesdayR)
library(stringr)
library(lubridate)
library(ggdark)
library(ggthemes)
```

This is my first TidyTuesday participation and oh how wonderful is the topic!

## Getting Data

The data this week came from FiveThirtyEight though the original source was superbowl-ads.com. It included information about the various themes in the past superbowl ads and their perception on YouTube. 

```{r message=FALSE, results=FALSE}
# Get the Data

# Read in with tidytuesdayR package 
# This loads the the dataset for the week of interest


tuesdata <- tidytuesdayR::tt_load('2021-03-02')
tuesdata <- tidytuesdayR::tt_load(2021, week = 10)

youtube <- tuesdata$youtube


```


## Data Wrangling 



```{r message=FALSE}
attach(youtube)

tempsuper<- youtube %>%
  mutate(mycategory = ifelse(animals & funny & !celebrity & !use_sex,"Animals and Humour",
                      ifelse(celebrity & use_sex,"Celebrities and Sex","N/A")))%>%
  select(mycategory,view_count, like_count , dislike_count)

tempsuper<- na.omit(tempsuper)

 tempsuper<- tempsuper%>%
   group_by(mycategory)%>%
  summarise(totviews = sum(view_count), totlikes = sum(like_count), totdislikes=sum(dislike_count))%>%
   filter(mycategory != "N/A")
 
tempsuper2 <- tempsuper   
     
 tempsuper <- select(tempsuper,-totviews)
 
 
 tempsuper <- pivot_longer(tempsuper,!mycategory, names_to = "classification", values_to = "value")
 
 tempsuper <- tempsuper%>%
   mutate(classification = str_replace(classification, "totlikes", "Total Likes"), 
       classification = str_replace(classification, "totdislikes", "Total Dislikes"))

 tempsuper <- tempsuper%>%
   mutate(classification = as.factor(classification))%>%
   mutate(classification = fct_relevel(classification,"Total Likes"))
 
 
 tempsuper2 <- tempsuper2 %>%
   mutate(ratio = totlikes/totdislikes)

```



## Data Visualization

The graphs are plotted as follows:

```{r message=FALSE}

ggplot(data = tempsuper, aes(x = mycategory, y = value, fill = classification)) +
  geom_bar(stat = "identity", position = position_dodge(), alpha = 0.75)  +
  scale_fill_brewer(palette = "Dark2")+
  labs(x = "\n Category", y = "Frequency\n", title = "\n              Animals and Humour or Celebrities and Sex? \n",fill=element_blank())+
  theme_minimal()
  

```

It would be more useful to look at the like to dislike ratios because the view counts are heavily unbalanced.

```{r message=FALSE}
ggplot(data = tempsuper2, aes(x = mycategory, y = ratio, fill = mycategory)) +
  geom_bar(stat = "identity", position = position_dodge(), alpha = 0.75)  +
  scale_fill_manual(values = c("orange","black"))+
  labs(x = element_blank(), y = "Ratio\n", title = "\n              Animals and Humour or Celebrities and Sex?\n                           Looking at like/dislike ratios \n", fill = "Category") +
  theme_minimal()+
  theme(axis.text.x = element_blank())
  
```



