---
title: "Steam Games TidyTuesday"
author: "Divyaanshu Panwar"
date: "17th March 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(tidytuesdayR)
library(stringr)
library(lubridate)
library(ggdark)
library(ggthemes)
```

## Getting Data

The data was originally from Steam by way of Kaggle and originally came from SteamCharts. The data was scraped and uploaded to Kaggle. The data from the `tidytuesday` GitHub is imported as follows :

```{r results=FALSE,message=FALSE}
# Getting the Data

# Reading in with tidytuesdayR package 
# This loads the dataset for the week of interest

tuesdata <- tidytuesdayR::tt_load('2021-03-16')
tuesdata <- tidytuesdayR::tt_load(2021, week = 12)

games <- tuesdata$games
```

## Data Wrangling 

On initial impressions it can be seen that some structuring of the data can be problematic, especially the date. So I change it to a usable format. Also some game names are very long and have popularized abbreviations so I use those.


```{r message=FALSE}
attach(games)

games <- games %>%
  unite(yearmonth, month:year)%>%
  mutate(date = yearmonth)%>%
  select(-yearmonth)

games$date <- str_replace_all(games$date, "_" , " ")

games <- games %>%
  mutate(gamename = str_replace(gamename, "PLAYERUNKNOWN'S BATTLEGROUNDS", "PUBG"), 
       gamename = str_replace(gamename, "Counter-Strike: Global Offensive", "CS:GO"))
```

## Info Gathering

I want to know about the most popular games on Steam on the basis of the overall average of the average number of players by month to use it to plot a graph later.

```{r message=FALSE}
temp2077 <- games
  
options(scipen = 999)

temp2077 <- temp2077 %>%
  group_by(gamename)%>%
  summarize(mean_avg = mean(avg))%>%
  arrange(desc(mean_avg))

temp2077 <- temp2077[1:4,]

```
## Data Visualization

Using the following code, I obtain the final dataset to use in creating the desired graph.

```{r message=FALSE}

games <- games %>%
  mutate(date = lubridate::my(date))

finaldata <- games %>%
  filter(gamename %in% temp2077$gamename)

```

The final graph is as follows : 

```{r message=FALSE}

ggplot(finaldata, aes(x=date, y=avg, fill=gamename))+
  geom_col(position="dodge")+
  labs(title= "The Most Popular Games on Steam by \nAverage Monthly Players", 
       y="Average number of players", x="Date")+
  scale_fill_manual("Name of Game",values = c("white","red","yellow","#0a9cf5"))+
  dark_mode(theme_fivethirtyeight())
  
  
```


See those small red columns on the bottom right? Yep. That's Cyberpunk 2077
